Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd

```{r, fig.width=15, fig.height=5, message=FALSE, warning=FALSE}
titlecount_timeline(subset(df0, catalog == "Fennica"), 
          "publisher", nmin = 500, mode = "n")$plot
```

@@

theme_set(theme_bw(20))
p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
     xlab("Publication year") +
     ylab("Title count frequency (%)") +
     #ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
     ggtitle(catalogue) +
     guides(fill = guide_legend(reverse = TRUE, title = "")) +
     scale_fill_brewer(palette="Paired")
pics[[catalogue]] <- p
}
library(gridExtra)
grid.arrange(pics[[1]], pics[[2]], nrow = 2)
```

>>>>

```{r, fig.width=15, fig.height=5, message=FALSE, warning=FALSE}
library(bibliographica)
titlecount_timeline(subset(df0, catalog == "Fennica"), 
          "publisher", nmin = 500, mode = "n")$plot
```

@@

theme_set(theme_bw(20))
p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
     xlab("Publication year") +
     ylab("Title count frequency (%)") +
     #ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
     ggtitle(catalogue) +
     guides(fill = guide_legend(reverse = TRUE, title = "")) +
     scale_fill_brewer(palette="Paired")
pics[[catalogue]] <- p
library(dplyr)
library(magrittr)
}
library(gridExtra)
grid.arrange(pics[[1]], pics[[2]], nrow = 2)
```
